Making Sequential Programs Deterministic

### 2019-04-05 randoop-case-study.tex
macros

\begin{itemize}
\item \textbf{Bug 1:}
  A use of \<HashSet> that the developers changed to \<LinkedHashSet>\commit{c975a9f7}.
The old code could cause a problem if a type variable's lower or upper
bound has a type parameter that the type variable itself does not have.
This situation does occur, even in Randoop's test suite.

\item \textbf{Bug 2:}
Dependency on the CLASSPATH environment variable in preference to the
classpath passed on the command line\commit{330e3c56}.
This could have led to incorrect behavior if a user set the environment variable.
The developers changed Randoop to not read the environment variable.

\item \textbf{Bug 3:}
Diagnostic output that printed a hash code for brevity, but should have had
deterministic output\commit{661a4970}.  By contrast to the first two bugs,
this one is not serious.

\item \textbf{Bug 4:}
Diagnostic output that printed a timestamp, but should have obeyed an
option about whether to do so\commit{a460df97}.  By contrast to the first
two bugs, this one is not serious.

>>>>

\begin{itemize}
\item \bugOne:
  A use of \<HashSet> that the developers changed to \<LinkedHashSet>\commit{c975a9f7}.
The old code could cause a problem if a type variable's lower or upper
bound has a type parameter that the type variable itself does not have.
This situation does occur, even in Randoop's test suite.

\item \bugTwo:
Dependency on the CLASSPATH environment variable in preference to the
classpath passed on the command line\commit{330e3c56}.
This could have led to incorrect behavior if a user set the environment variable.
The developers changed Randoop to not read the environment variable.

\item \bugThree:
Diagnostic output that printed a hash code for brevity, but should have had
deterministic output\commit{661a4970}.  By contrast to the first two bugs,
this one is not serious.

\item \bugFour:
Diagnostic output that printed a timestamp, but should have obeyed an
option about whether to do so\commit{a460df97}.  By contrast to the first
two bugs, this one is not serious.
